Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-26 man/figures/bai_cronos.Rmd
update figures and chronos

---
output: 
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
```

```{r, echo=FALSE}
show_text <- FALSE
```

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas correspond to standard error of the mean. Number of series are displayed in the upper plot. We only show years replicated with # series > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) .AREGLAR ESTO
##### 
```{r, warning=FALSE, echo=FALSE}
cro_sites <- read.csv(here("data/cronos_medias", "cronos_sites.csv"), header = TRUE, sep = ',')

colores <- c('#7570b3','#e7298a','#1b9e77')
# colores <- c('#33a02c', '#984ea3', '#a65628')

@@

mCaH <- lm(bai_mean ~ year, dfCaH)
summary(mCaH)
r2caH <- format(summary(mCaH)$r.squared, digits = 3)
pCaH <- lmp(mCaH)

@@

mCaL <- lm(bai_mean ~ year, dfCaL)
summary(mCaL)
r2caL <- format(summary(mCaL)$r.squared, digits = 3)
pCaL <- lmp(mCaL)

@@

mSJ <- lm(bai_mean ~ year, dfSJ)
summary(mSJ)
r2SJ <- format(summary(mSJ)$r.squared, digits = 3)
pSJ <- lmp(mSJ)
```

```{r, warning=FALSE, out.extra='angle=90'}

# cores 
cronos_bai <- cro_sites %>% filter(n_trees >5) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        axis.text.x=element_text(size=6),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020)) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-High'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-Low'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'SJ'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE)

  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site)) 
samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=6),
        # axis.text.x=element_blank(),
        # axis.ticks.x=element_blank(), 
        # plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")
        ) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10))  
  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))

plot_bai_s <- samp + cronos_bai + plot_layout(ncol=1, heights = c(0.15, 0.85))
plot_bai_s
```

>>>>

---
output: 
  word_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
```

```{r data}
cro_sites <- read.csv(here("data/cronos_medias", "cronos_sites.csv"), header = TRUE, sep = ',')

@@

mCaH <- lm(bai_mean ~ year, dfCaH)
r2caH <- format(summary(mCaH)$r.squared, digits = 3)
pCaH <- lmp(mCaH)

@@

mCaL <- lm(bai_mean ~ year, dfCaL)
r2caL <- format(summary(mCaL)$r.squared, digits = 3)
pCaL <- lmp(mCaL)

@@

mSJ <- lm(bai_mean ~ year, dfSJ)
r2SJ <- format(summary(mSJ)$r.squared, digits = 3)
pSJ <- lmp(mSJ)

lms <- data.frame(year = as.numeric(c(2018, 2018, 2018)),
                     site = c("CA-Low", "CA-High", "SJ"), 
                     r2 = as.numeric(c(r2caL, r2caH, r2SJ)),
                     pvalue = as.numeric(round(c(pCaL, pCaH, pSJ), 4)),
                     y = as.numeric(c(as.numeric(predict(mCaL)[40]), 
                           as.numeric(predict(mCaH)[40]), 
                           as.numeric(predict(mSJ)[40]))))
lms$y <- lms$y / 100
lms <- lms %>% mutate(
  pc = ifelse(pvalue < 0.001, "p < 0.001", as.character(paste0("p = ", pvalue))),
  label = round(r2,3))

```

```{r plot_configure}
# colores <- c("#B2DF8A","#1F78B4","#A6CEE3")
# colores <- c('#7570b3','#e7298a','#1b9e77')
# colores <- c('#33a02c', '#984ea3', '#a65628')
colores <- c("#000000", "#0072B2", "#D55E00") 
```

```{r plot_cronobai}
colores <- c("#B2DF8A","#1F78B4","#A6CEE3")
colores <- c("#000000", "#0072B2", "#D55E00")

# cores 
cronos_bai <- cro_sites %>% filter(nseries > 5) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.4, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020), sec.axis = dup_axis()) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-High'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-Low'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'SJ'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5)  +
  geom_text_repel(data = lms, 
                  aes(x=year, y = y, colour = site, label = label),
                  nudge_x = Inf, 
                  direction = "x", show.legend = FALSE, 
                  size = 3) + 
  theme(panel.grid = element_blank(),
        axis.text.x=element_text(size=6),
        legend.position = c(0.2,.8),
        strip.background = element_blank(),
        axis.title.x.top = element_blank(), 
        axis.text.x.top = element_blank())  
```

```{r plot_samp}
  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site)) 
samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020), 
                     sec.axis = dup_axis(), position = "top") +
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x.top = element_text(size=6), 
        axis.text.x.bottom = element_blank(), 
        # axis.text.x=element_blank(),
        # axis.ticks.x=element_blank(), 
        # plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")
        ) 
  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))
```

```{r plot_all}
plot_bai_s <- samp + cronos_bai + plot_layout(ncol=1, heights = c(0.15, 0.85))

```

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *orange*) and southern ones: low-elevation (CA-Low; *blue*) and high-elevation (CA-High, *black*) sites. Shading areas correspond to standard error of the mean. Number of series are displayed in the upper plot. We only show years replicated with # series > 5. Linear trends since 1975 are shown all sites (numbers indicate $r^2$ values).

```{r out_plot, fig.height = 5, fig.width=7, dpi = 300, out.width = 0.8}
plot_bai_s
```

### 2018-11-26 man/figures/corr_plot_years.Rmd
update figures and chronos

---
output: 
  word_document:
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
library("GGally")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

```{r, echo=FALSE}
show_text <- FALSE
```
##### 
**Appendix S5.** Correlation between indices of resilience (*Rt*, resistance; *Rc*, recovery; *Rs*, Resilience) using periods of several lengths (2, 3 and 4 years after a drought). Top plots (a, b and c) showing the resilience indices of greenness (EVI) to drought; and bottom plots (d, e, f) the resilience indices of tree-growth (BAI) to drought.

```{r}

corBai <- read.csv(file=here("/out/correla_resilience/", "correla_window_size.csv"), header = TRUE)
corEvi <- read.csv(file=here("/out/correla_resilience/", "correla_window_size_evi.csv"), header = TRUE)
corRwi <- read.csv(file=here("/out/correla_resilience/", "correla_window_size_rwi.csv"), header = TRUE)

@@

cor_rte <- generaMatrix(corEvi, 'rt')
cor_rce <- generaMatrix(corEvi, 'rc')
cor_rse <- generaMatrix(corEvi, 'rs')

correP <- function(df, mytitle, ...){
  require(ggplot2)
  require(ggcorrplot)

  p <- ggcorrplot(df, method = "square", type ='upper', 
                  outline.color = "black", colors = "white",
                  ggtheme = theme_minimal, 
                  lab = TRUE, lab_size = 12,
                  title = mytitle, show.legend = FALSE, 
                  tl.cex = 10)
  p <- p + theme(plot.title = element_text(size = 14, face = "bold.italic"))
  p      
}

g_rt <- correP(cor_rt, 'BAI Rt')
g_rc <- correP(cor_rc, 'BAI Rc')
g_rs <- correP(cor_rs, 'BAI Rs')
g_rte <- correP(cor_rte, 'EVI Rt')
g_rce <- correP(cor_rce, 'EVI Rc')
g_rse <- correP(cor_rse, 'EVI Rs')

(g_rte + g_rce + g_rse) / (g_rt + g_rc + g_rs) + plot_layout(nrow=2) + plot_annotation(tag_levels = c('a'))
```

>>>>

---
output: 
  word_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
# library("GGally")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

```{r data}
corBai <- read.csv(file=here("/out/correla_resilience/", "correla_window_size.csv"), header = TRUE)
corEvi <- read.csv(file=here("/out/correla_resilience/", "correla_window_size_evi.csv"), header = TRUE)
corRwi <- read.csv(file=here("/out/correla_resilience/", "correla_window_size_rwi.csv"), header = TRUE)

@@

cor_rte <- generaMatrix(corEvi, 'rt')
cor_rce <- generaMatrix(corEvi, 'rc')
cor_rse <- generaMatrix(corEvi, 'rs')
```

```{r plot_function}
correP <- function(df, mytitle, ...){
  require(ggplot2)
  require(ggcorrplot)

  p <- ggcorrplot(df, method = "square", type ='upper', 
                  outline.color = "black", colors = "white",
                  ggtheme = theme_minimal, 
                  lab = TRUE, lab_size = 5,
                  title = mytitle, show.legend = FALSE, 
                  tl.cex = 7,
                  tl.srt = 1)
  p <- p + theme(plot.title = element_text(size = 10, face = "bold.italic"),
                 panel.grid = element_blank(),
                 axis.text.x = element_text(hjust = 0.5)) + scale_x_discrete(position = "top") 
  p      
}
```

```{r plot}
g_rt <- correP(cor_rt, 'BAI Rt')
g_rc <- correP(cor_rc, 'BAI Rc')
g_rs <- correP(cor_rs, 'BAI Rs')
g_rte <- correP(cor_rte, 'EVI Rt')
g_rce <- correP(cor_rce, 'EVI Rc')
g_rse <- correP(cor_rse, 'EVI Rs')

g <- (g_rte + g_rce + g_rse) / (g_rt + g_rc + g_rs) + plot_layout(nrow=2) + plot_annotation(tag_levels = c('a'))
```

**Figure S5.** Correlation between indices of resilience (*Rt*, resistance; *Rc*, recovery; *Rs*, Resilience) using periods of several lengths (2, 3 and 4 years after a drought). Top plots (a, b and c) showing the resilience indices of greenness (EVI) to drought; and bottom plots (d, e, f) the resilience indices of tree-growth (BAI) to drought.

```{r plot_out, fig.width=6, dpi = 300, out.width = 0.8} 
g
```

### 2018-11-26 man/figures/correla_boot_sites.Rmd
update figures and chronos

---
output: 
  word_document:
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

@@

```{r, echo=FALSE}
show_text <- FALSE
```

@@

```{r}
correla  <- read.csv(file=here("/data/correla_ventanas_temporales/", "correla_chronos.csv"), header = TRUE)

correla <- correla %>% 
  mutate(
    name_comparison = as.factor(case_when(
      name_comparison == "caH-caL" ~ "CAHigh - CALow",
      name_comparison == "sj-caL" ~ "SJ - CALow",
      name_comparison == "sj-caH" ~ "SJ - CAHigh")))

correla_sitesSJCALH  <- correla %>% 
  filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate)) + 
  geom_line(aes(colour=name_comparison), size = 1.4) + 
  theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_ribbon(aes(ymax=ci_upper, ymin=ci_lower, fill=name_comparison), alpha=0.3) + 
  scale_fill_colorblind() + 
  scale_color_colorblind() +
  theme(legend.position = c(.8,.9), 
        legend.title = element_blank(), 
        legend.text = element_text(size = 14),
        panel.grid = element_blank(), 
        axis.title = element_text(size = 14), 
        axis.text = element_text(size = 11))

correla_sitesSJCALH

```

>>>>

---
output: 
  word_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")

@@

@@

```{r data}
correla  <- read.csv(file=here("/data/correla_ventanas_temporales/", "correla_chronos.csv"), header = TRUE)

correla <- correla %>% 
  mutate(
    name_comparison = as.factor(case_when(
      name_comparison == "caH-caL" ~ "CAHigh - CALow",
      name_comparison == "sj-caL" ~ "SJ - CALow",
      name_comparison == "sj-caH" ~ "SJ - CAHigh")))
```

```{r plot}
correla_sitesSJCALH  <- correla %>% 
  filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate)) + 
  geom_line(aes(colour=name_comparison), size = 1) + 
  theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_ribbon(aes(ymax=ci_upper, ymin=ci_lower, fill=name_comparison), alpha=0.3) + 
  scale_fill_colorblind() + 
  scale_color_colorblind() +
  theme(legend.position = c(.8,.87), 
        legend.title = element_blank(), 
        legend.text = element_text(size = 6),
        panel.grid = element_blank(), 
        axis.title = element_text(size = 10), 
        axis.text = element_text(size = 7),
        legend.background = element_blank())
```

```{r plot_out, fig.width=6, dpi = 300, out.width = 0.8} 
correla_sitesSJCALH
```

### 2018-11-26 man/figures/gc_perc_trees.Rmd
update figures and chronos

pgc_median50 <- gc_treesMed50 %>% 
  filter(total_tree > 2) %>% 
  ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill=colorpositivo, colour=colorpositivo, 
           stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill=colornegativo, colour=colornegativo, 
           stat = "identity", position = "dodge") +
  geom_line(aes(x=year, y=total_tree), colour = 'black', size = 0.4) + 
  theme_bw() + ylab('% of trees') + xlab("Year") + 
  geom_hline(yintercept=0, alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, alpha=.4) +
  scale_x_continuous(breaks = xrange) +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 50),
                     sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  facet_rep_wrap(~site_sorted, nrow = 3, 
                 repeat.tick.labels = TRUE, labeller = as_labeller(label_site)) +
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        strip.text = element_blank(),
        axis.text.y.left = element_text(size=6),
        axis.text.y.right  = element_text(size=5),
        axis.text.x = element_text(size=6),
        axis.title = element_text(size = 9))

>>>>

pgc_median50 <- gc_treesMed50 %>% 
  filter(total_tree > 2) %>% 
  ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill=colorpositivo, colour=colorpositivo, 
           stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill=colornegativo, colour=colornegativo, 
           stat = "identity", position = "dodge") +
  geom_line(aes(x=year, y=total_tree*2), colour = 'black', size = 0.2) + 
  theme_bw() + ylab('% of trees') + xlab("Year") + 
  geom_hline(yintercept=0, alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, alpha=.4) +
  scale_x_continuous(breaks = xrange) +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 50),
                     sec.axis = sec_axis(~., name = '# trees', breaks = c(0,15,30))) +
  facet_rep_wrap(~site_sorted, nrow = 3, 
                 repeat.tick.labels = TRUE, labeller = as_labeller(label_site)) +
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        strip.text = element_blank(),
        axis.text.y.left = element_text(size=6),
        axis.text.y.right  = element_text(size=5),
        axis.text.x = element_text(size=6),
        axis.title = element_text(size = 9))
